Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars

### 2014-10-21 drafts/cfp/draft.tex
Changes and fixed problem with bib file.

\setlength{\droptitle}{-4em}   % This is your set screw

@@

\begin{document}
\vspace{-10cm}
\maketitle
\vspace{-2em}

@@

\begin{figure}[t]
		\includegraphics[width=\linewidth]{lpn/lpn.pdf}
		\caption{A schematic LPN.}
		\label{fig:architecture}
\end{figure}

@@

\section{Implementation \label{sec:implementation}}

@@

\begin{table}[t]
\begin{tabular}{>{\footnotesize} l >{\footnotesize} l}
  Question & $K=4$ \\ \hline
  after twenty comes \underline{\hspace{1cm}}? & twenty one \checkmark \\
  after forty five comes \underline{\hspace{1cm}}? & forty six \checkmark \\
  after forty seven comes \underline{\hspace{1cm}}? & forty eight  \checkmark \\
  after forty nine comes \underline{\hspace{1cm}}? & forty ten $\times$ \\
  after fifty nine comes \underline{\hspace{1cm}}? & fifty ten $\times$ \\
  after sixty one comes \underline{\hspace{1cm}}? & sixty two \checkmark \\
  after sixty three comes \underline{\hspace{1cm}}? & sixty four \checkmark \\
  after sixty four comes \underline{\hspace{1cm}}? & sixty five \checkmark \\
  after sixty five comes \underline{\hspace{1cm}}? & sixty six \checkmark \\
  after sixty nine comes \underline{\hspace{1cm}}? & sixty ten $\times$ \\
  after seventy three comes \underline{\hspace{1cm}}? & seventy four \checkmark \\
  after seventy nine comes \underline{\hspace{1cm}}? & seventy ten $\times$ \\
  after ninety five comes \underline{\hspace{1cm}}? & ninety six \checkmark \\
  before twenty three comes \underline{\hspace{1cm}}? & twenty two \checkmark \\
  before thirty comes \underline{\hspace{1cm}}? & thirty eighty $\times$ \\
  before thirty eight comes \underline{\hspace{1cm}}? & thirty seven \checkmark \\
  before forty one comes \underline{\hspace{1cm}}? & forty \checkmark \\
  before fifty three comes \underline{\hspace{1cm}}? & fifty two \checkmark \\
  before sixty eight comes \underline{\hspace{1cm}}? & sixty seven \checkmark \\
  before seventy two comes \underline{\hspace{1cm}}? & seventy one \checkmark \\
  before seventy three comes \underline{\hspace{1cm}}? & seventy two \checkmark \\
  before eighty five comes \underline{\hspace{1cm}}? & eighty four \checkmark \\
  before ninety two comes \underline{\hspace{1cm}}? & ninety one \checkmark \\
  before ninety three comes \underline{\hspace{1cm}}? & ninety two \checkmark \\
  before ninety five comes \underline{\hspace{1cm}}? &ninety four \checkmark \\
\end{tabular}
\caption{examples of generalization for held out sentences after learning over 4 latent predicates}
\label{tab:results}
\end{table}

@@

\section{Discussion}

>>>>

\setlength{\droptitle}{-6em}   % This is your set screw

@@

\begin{document}
\vspace{-10cm}
\maketitle
\vspace{-6em}

@@

\begin{figure}[t]
		\includegraphics[width=\linewidth]{lpn/lpn.pdf}
		\caption{The architecture and rules of a schematic LPN.}
		\label{fig:architecture}
\end{figure}

@@

\vspace{-1em}
\section{Implementation \label{sec:implementation}}

@@

\begin{table}[t]
\begin{tabular}{>{\footnotesize} l >{\footnotesize} l}
  Question & $K=4$ \\ \hline
  after twenty comes \underline{\hspace{1cm}}? & twenty one \checkmark \\
  after forty five comes \underline{\hspace{1cm}}? & forty six \checkmark \\
  after forty seven comes \underline{\hspace{1cm}}? & forty eight  \checkmark \\
  after forty nine comes \underline{\hspace{1cm}}? & forty ten $\times$ \\
  after fifty nine comes \underline{\hspace{1cm}}? & fifty ten $\times$ \\
  after sixty one comes \underline{\hspace{1cm}}? & sixty two \checkmark \\
  after sixty three comes \underline{\hspace{1cm}}? & sixty four \checkmark \\
  after sixty four comes \underline{\hspace{1cm}}? & sixty five \checkmark \\
  after sixty five comes \underline{\hspace{1cm}}? & sixty six \checkmark \\
  after sixty nine comes \underline{\hspace{1cm}}? & sixty ten $\times$ \\
  after seventy three comes \underline{\hspace{1cm}}? & seventy four \checkmark \\
  after seventy nine comes \underline{\hspace{1cm}}? & seventy ten $\times$ \\
  after ninety five comes \underline{\hspace{1cm}}? & ninety six \checkmark \\
  before twenty three comes \underline{\hspace{1cm}}? & twenty two \checkmark \\
  before thirty comes \underline{\hspace{1cm}}? & thirty eighty $\times$ \\
  before thirty eight comes \underline{\hspace{1cm}}? & thirty seven \checkmark \\
  before forty one comes \underline{\hspace{1cm}}? & forty \checkmark \\
  before fifty three comes \underline{\hspace{1cm}}? & fifty two \checkmark \\
  before sixty eight comes \underline{\hspace{1cm}}? & sixty seven \checkmark \\
  before seventy two comes \underline{\hspace{1cm}}? & seventy one \checkmark \\
  before seventy three comes \underline{\hspace{1cm}}? & seventy two \checkmark \\
  before eighty five comes \underline{\hspace{1cm}}? & eighty four \checkmark \\
  before ninety two comes \underline{\hspace{1cm}}? & ninety one \checkmark \\
  before ninety three comes \underline{\hspace{1cm}}? & ninety two \checkmark \\
  before ninety five comes \underline{\hspace{1cm}}? &ninety four \checkmark \\
\end{tabular}
\caption{Viterbi completions of held-out sentences to evaluate an LPN with 4 latent predicates in the number domain.}
\label{tab:results}
\end{table}

@@

\vspace{-1em}
\section{Discussion}
